### 2016-10-31 paper/evaluation.tex
Working on RQ2

\newcommand{\RQONE}{How prevalent is the occurence of time-consuming
regression tests in open-source projects?}
\newcommand{\RQTWO}{What is the distribution of CPU and IO bound
regression tests from the sample set?}
\newcommand{\RQTHREE}{What is the proportion of \Fix{time-consuming?}
test cases per project?}
\newcommand{\RQFOUR}{How often developers use the parallelism features
from build manager systems to improve performance on test execution?}

\newcommand{\rqA}{\textbf{RQ1.} \RQONE}
\newcommand{\rqB}{\textbf{RQ2.} \RQTWO}
\newcommand{\rqC}{\textbf{RQ3.} \RQTHREE}
\newcommand{\rqD}{\textbf{RQ4.} \RQFOUR}

\begin{itemize}
    \item \rqA
    \item \rqB
    \item \rqC
    \item \rqD
\end{itemize}

The first research question addresses the distribution of subjects per
elapsed time to execute regression tests. We are interested on
identifying time-consuming test suites for further investigation. The
second research question addresses addresses \Fix{...}. The third
research question addresses the distribution of \Fix{...}. Finally,
the fourth research question investigates the relevance of supporting
parallel execution on builder tools.

@@

%% \begin{itemize}
%%     \item \RQONE
%% \end{itemize}

@@

\subsection{Answering research question RQ2}
\label{sec:rqtwo}

%% \begin{itemize}
%%     \item \RQTWO
%% \end{itemize}

@@

\subsection{Answering research question RQ3}
\label{sec:rqthree}

%% \begin{itemize}
%%     \item \RQTHREE
%% \end{itemize}

>>>>

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression tests in open-source projects?}
\newcommand{\RQB}{What is the distribution of CPU and IO bound
regression tests from the sample set?}
\newcommand{\RQC}{How the execution time is distributed among test
cases?}
\newcommand{\RQD}{How often developers use the parallelism features
from build manager systems to improve performance on test execution?}

\newcommand{\rqOne}{\textbf{RQ1.} \RQA}
\newcommand{\rqTwo}{\textbf{RQ2.} \RQC}
\newcommand{\rqThree}{\textbf{RQ3.} \RQB}
\newcommand{\rqFour}{\textbf{RQ4.} \RQD}

\begin{itemize}
    \item \rqOne
    \item \rqTwo
    \item \rqThree
    \item \rqFour
\end{itemize}

The first research question addresses the distribution of subjects per
elapsed time to execute regression tests. We are interested on
identifying time-consuming test suites for further investigation. The
second research question addresses the distribution of execution time
per test case for each project. The rationale is that if the time cost
of a regression test is equally distributed among test cases, the
execution cost could be potentially improved by running tests in
parallel (in contrast to the scenario where only one test case
dominates most of the execution time).

@@

\begin{itemize}
    \item \RQA
\end{itemize}

@@

\subsection{Answering research question RQ2}
\label{sec:rqTwo}

\begin{itemize}
    \item \RQC
\end{itemize}

To evaluate the distribution of execution time, we collected from the
test report (\ie, Surefire XML file) the elapsed time to execute
each test case and \Fix{...to be continued...}.

\subsection{Answering research question RQ3}
\label{sec:rqThree}

\begin{itemize}
    \item \RQB
\end{itemize}

@@
